% !TEX program = xelatex
\documentclass[margin]{letter}
\setlength{\textwidth}{5.0in} % set width of text portion

\usepackage{fontspec}
% \setmainfont{Calibri}

\signature{Kamin Horvath}

\begin{document}

\begin{letter}{Application Committee}
    \opening{Dear Sir or Madam,}
    I am excited and thankful for being considered for this position. I hope to bring a wealth of knowledge and experience to the role.
    Having been in the mechanical and HVAC industry for over 5 years, I have worked in a variety of roles that have allowed me the rare opportunity
    to learn from all ends of the trade. I began with five years experience working for a manufacturer's representative where I learned about sizing and applications of
    hydronic equipment, as well as gaining expertise in working with engineers, plans, and performing takeoffs and estimates. 
    
    From there, I've spent another 3 years in the mechanical contracting world, where I've learned the other side of the trade - how to apply the equipment and tools I had learned about to real world scenarios.
    I gained experience in sales to commercial and industrial end users, and learned the full cycle of project management - from pre-sale, to estimating material and labor, to project execution and closeout. I've also gained experience in working
    ouside of the scope of just mechanical sales, working with electrical, plumbing, controls, and overall general contracting.

    Overall, this wealth of experience and knowledge has made me a well rounded candidate, and I believe that I can use this to better myself in this new position, as well as to help elevate others, and the company as a whole.

    Thank you again for your consideration, and I hope to hear back from you soon.
    \closing{Sincerely,}
\end{letter}
\end{document}




