% !TEX program = xelatex
% LaTeX resume using res.cls
\documentclass[margin]{res}
\setlength{\textwidth}{5.25in} % set width of text portion

%\usepackage{fontspec}
\usepackage{thaispec}
\usepackage{setspace}

\singlespacing

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Kamin G. Horvath}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Atlanta, GA}
 \moveleft.5\hoffset\centerline{(470) 421-8281}
 \moveleft.5\hoffset\centerline{kamin@kghorvath.com}


\begin{resume}
 
\section{OBJECTIVE}  To expand on my experience and continue to grow my skillset in project management, project estimating, sales, and technical knowledge in the industry.
            
\section{EXPERIENCE} 
    {\sl Project Estimator/Business Development Manager} \hfill February 2022-November 2024\footnote{Due to financial reasons, position was eliminated from the company in November 2024} \\
    ABM, Cumming, GA
    \begin{itemize}  \itemsep -2pt %reduce space between items
    \item {\sl Project Estimator (2023-2024)}
      \begin{itemize}
            \item[$\circ$] Scouting, estimating, and presenting mechanical contracting projects and maintenance agreements to commercial and industrial customers.
            \item[$\circ$] Experience in designing and sizing HVAC systems and equipment for a wide variety of public, commercial and industrial applications in Georgia, Alabama, and Virginia.
            \item[$\circ$] Project and customer types include industrial plants, government buildings, schools, office spaces, and convention centers. Notable projects include:
              \begin{itemize}
              \item Marukan Vinegar - Chilled Water Piping Replacement: \$1.2 million
              \item Montgomery County, GA - Courthouse HVAC Renovation: \$761,000
              \item Atlanta VA Medical Center - Mobile Lab Exhaust: \$250,000
              \item Georgia World Congress Center - AHU PM Budget: \$520,000
              \end{itemize}
%            \item[$\circ$] Estimate a wide variety of different systems including unitary, hydronic, and VRF. Examples of projects include cooling tower, chiller, boiler, package units, and VRF system installations.
            \item[$\circ$] Work closely with the project management team to ensure that project is successfully handed off and executed once accepted.
            \item[$\circ$] Utilize a variety of different tools to perform estimates including RSMeans, Bluebeam Vue, Microsoft Project, GNU Octave, and GNU Emacs.
      \end{itemize}
      \item {\sl Business Development Manager (2022-2023)}
      \begin{itemize}
            \item[$\circ$] Experience in prospecting to new clients, and working with existing clients on new mechanical projects.
            \item[$\circ$] In addition to projects, priced HVAC maintenance agreements using PriceBuilder tool.
            \item[$\circ$] Prospected, estimated, sold, and helped manage own projects. Notable prospected projects include:
              \begin{itemize}
                \item Amazon DGT8 - New Gas Pipe - \$60,000
                \item Blue Bird - Paint Shop HVAC - \$300,000
                \item YMCA of Metro Atlanta - PTAC Replacement - \$52,000
              \end{itemize}
            \item[$\circ$] In addition to core business, also assisted in selling other ABM units such as electrical, EV charging, and janitorial.  
            \end{itemize}
            \end{itemize}
            
    {\sl Assistant Project Manager} \hfill February 2020-February 2022 \\
 	    Maxair Mechanical, Marietta, GA
        \begin{itemize}  \itemsep -2pt %reduce space between items
            \item Selling, estimating, and managing mechanical contracting project as part of Direct for Owner (DFO) team. Primarily selling and running jobs directly for end clients, where Maxair is the general contractor. Began assisting other project managers and migrated after 1 year to selling and managing own projects.
            \item Worked on anywhere between 5-10 projects at a time.
            \item Responsible for managing projects from pre-construction to completion. Responsibilities as full PM including managing both logistics and financials of projects.
            \item Worked with tools including Microsoft Project, LibreProject, and Sage Construction.
            \item Range of projects sold, estimated, and managed included equipment replacements, and new system retrofits in existing commercial and industrial facilities. Notable projects sold and managed include:
              \begin{itemize}
                \item[*] Southern Power Plant Franklin - VFD House HVAC - \$100,000
                \item[*] Chattahoochee Tech - Boiler Plant Replacement - \$150,000
                \item[*] Columbus State University - Richards Hall AHU Replacements - \$200,000
                \item[*] City of Smyrna - Jail Domestic HW Piping Replacement - \$100,000
              \end{itemize}
            \item Coordination of all parts of the job including equipment, labor, subcontractors, scheduling, permitting, and startup. Worked with a variety of trades and subcontractors to bring project to closeout and completion.
            \end{itemize}

    {\sl Technical Engineering Sales Support} \hfill May 2015-February 2020 \\
        James M. Pleasants Co., Peachtree Corners, GA
        \begin{itemize}  \itemsep -2pt %reduce space between items
            \item Sized and estimated hydronic equipment for engineers, and perfmed mechanical takeoffs and quotes for contractors.
            \item Assembled and priced the majority of projects for Georgia territory. Notable projects include:
              \begin{itemize}
              \item[*] Children's Healthcare of Atlanta Arthur M. Blank Hospital - New Mechanical Room Equipment
              \item[*] Gwinnett County Public Schools - Water Source Heat Pump Replacements (various schools)
              \item[*] Hartsfield-Jackson Atlanta International Airport - Domestic Terminal AHU and Concourse E Pump Replacements
              \item[*] Georgia Institute of Technology - Steam Boiler Replacement
              \end{itemize}
            \item Range of systems priced included pumps, cooling towers, water source heat pumps, boilers, and fan coil units. Brands represented included Bell \& Gossett, Baltimore Aircoil, Climatemaster, Lochinvar, and Whalen.
            \item Tools used include ESP Systemwize and PeopleSoft to size equipment, generate submittals, and produce customer proposals.
%            \item Scope of successful proposals ranged up to several million dollars worth of material.
            \end{itemize}
 
%    {\sl Supervisor Assistant} \hfill          May 2014-May 2015 \\
%        Town of Blacksburg, Blacksburg, VA
%        \begin{itemize}  \itemsep -2pt %reduce space between items
%            \item Supervised day-to-day operations for Blacksburg Transit, the public transit department of the town. Primary duties were office support, dispatching, trip scheduling, and system oversight.
%            \item Secondary duties in opening/closing transit garage, customer assistance, assigning and fueling vehicles, preparing manifests and bulletins, accident documentation, and roadside response.
%            \end{itemize} 

\section{EDUCATION} {\sl B.Sc.,} Mechanical Engineering \hfill  May 2015 \\
    Virginia Tech, Blacksburg, VA
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Designed, constructed, and tested a portable dental chair as part of a senior design group project, coordinating with the University at Buffalo School of Dental Medicine's community outreach program.
    \end{itemize}

\section{SKILLS}
    {\sl Language:} Basic knowledge of Thai (ไทย) written and spoken language. \\
    {\sl Certifications:} OSHA 30 certificate, Pre-IPM Project Management certificate
    {\sl Memberships:} ASHRAE Atlanta Chapter
    {\sl Personal Skills:} Self-taught knowledge in computer science and technology
    \begin{itemize} \itemsep -2pt
    \item Written a number of coding projects, including my personal website and this \LaTeX{} resume. 
    \item Knowledge in administering Windows, Linux, and Unix systems. Maintain a number of hosted services including my personal website, and a Mastodon instance.
    \end{itemize}

\end{resume}
\end{document}




