% !TEX program = xelatex
% LaTeX resume using res.cls
\documentclass[margin]{res}
\setlength{\textwidth}{5.0in} % set width of text portion

\usepackage{fontspec}
% \setmainfont{Calibri}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Kamin G. Horvath}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{4359 Vista Creek Ln}
 \moveleft.5\hoffset\centerline{Powder Springs, GA 30127}
 \moveleft.5\hoffset\centerline{(470) 421-8281}
  \moveleft.5\hoffset\centerline{kamin@kghorvath.com}


\begin{resume}
 
\section{OBJECTIVE}  To expand on my experience and continue to grow in sales and technical knowledge in the mechanical contracting and HVAC industry.
            
\section{EXPERIENCE} 
    {\sl Assistant Project Manager} \hfill February 2020-Present \\
 	    Maxair Mechanical, Marietta, GA
        \begin{itemize}  \itemsep -2pt %reduce space between items
            \item Selling, estimating, and managing mechanical contracting projects as part of Direct for Owner (DFO) team. Responsible for selling and managing projects from pre-construction to completion.
            \item Coordination of all parts of the job including equipment, labor, subcontractors, scheduling, permitting, and startup.
            \item Experience in outside sales to new and existing customer base.
	   \item Sold and managed successful projects with several large entities including Southern Company, the City of Smyrna, Kohl's, and Richmont Graduate University
            \item In 2021, achieved year end sales goal of \$1,000,000 by September. Expected to finish the year 2021 with \$1,500,000 in project sales.
            \end{itemize}

    {\sl Technical Engineering Sales Support} \hfill November 2016-February 2020 \\
        James M. Pleasants Co., Peachtree Corners, GA
        \begin{itemize}  \itemsep -2pt %reduce space between items
            \item Duties included sizing hydronic equipment for engineers, and performing mechanical takeoffs and quotes for contractors.
            \item Responsible for assembling design-build and plan and spec proposals for Georgia territory.
            \item Scope of successful proposals ranged up to \$1,000,000. Contributed to making Georgia branch the most successful in the company.
            \end{itemize}

    {\sl Inside Sales Representative} \hfill May 2015-November 2016 \\
 	    James M. Pleasants Co., Greensboro, NC
        \begin{itemize}  \itemsep -2pt %reduce space between items
            \item Assisted customers in identifying, price quoting, and purchasing new HVAC equipment and accessories.
            \item Provided technical support and engineering knowledge for clients with existing systems and equipment.
            \end{itemize}
 
%    {\sl Supervisor Assistant} \hfill          May 2014-May 2015 \\
%        Town of Blacksburg, Blacksburg, VA
%        \begin{itemize}  \itemsep -2pt %reduce space between items
%            \item Supervised day-to-day operations for Blacksburg Transit, the public transit department of the town. Primary duties were office support, dispatching, trip scheduling, and system oversight.
%            \item Secondary duties in opening/closing transit garage, customer assistance, assigning and fueling vehicles, preparing manifests and bulletins, accident documentation, and roadside response.
%            \end{itemize} 

\section{EDUCATION} {\sl B.Sc.,} Mechanical Engineering \hfill  May 2015 \\
    Virginia Tech, Blacksburg, VA
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Designed, constructed, and tested a portable dental chair as part of a senior design group project, coordinating with the University at Buffalo School of Dental Medicine's community outreach program.
    \end{itemize}
 
\section{SKILLS} {\sl Certifications:} 
        \begin{itemize}  \itemsep -2pt %reduce space between items
	\item OSHA 30-Hour trained
	\item MCAA Pre-IPM Project Management Program
	\end{itemize}
  {\sl Memberships:}
          \begin{itemize}  \itemsep -2pt %reduce space between items
	\item ASHRAE Atlanta Chapter member since 2016
	\end{itemize}
 

%\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            %{\it Member}, Society of Asian Students and Engineers (SASE)
            %\begin{itemize}
            %\item Participated in community service projects sponsored by SASE.
            %\end{itemize}
	  %{\it Contributor}, Prof. Anthony Ferrar's Virginia Tech Green Initiative
	% \begin{itemize}
           % \item Recruited new members into the Green Initiative, which sought to reduce the carbon footprint of the Virginia Tech campus.


\end{resume}
\end{document}




