% !TEX program = xelatex
% LaTeX resume using res.cls
\documentclass[margin]{res}
\setlength{\textwidth}{5.0in} % set width of text portion

\usepackage{fontspec}
% \setmainfont{Calibri}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Kamin G. Horvath}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{1500-208 Brandonshire Court}
 \moveleft.5\hoffset\centerline{Greensboro, NC 27409}
 \moveleft.5\hoffset\centerline{(571) 499-0544}
  \moveleft.5\hoffset\centerline{kamin.horvath@vt.edu}


\begin{resume}
 
\section{OBJECTIVE}  A position in the field of Mechanical Engineering with an emphasis on energy efficiency and sustainability as well as Fluid Mechanics. A long-term goal of
	moving into a leadership role, based on proven experience.
 

\section{EDUCATION} {\sl B.Sc.,} Mechanical Engineering \hfill  May 2015 \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
              Virginia Tech, Blacksburg, VA
              \begin{itemize}  \itemsep -2pt %reduce space between items
              \item Designed, constructed, and tested a portable dental chair as part of a senior design group project, coordinating with the University at Buffalo School of Dental Medicine's community outreach program.
              \end{itemize}
               
               
 \section{EXPERIENCE} 
 {\sl Inside Sales Representative} \hfill May 2015-Present \\
 	James M. Pleasants Co., Greensboro, NC
   \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item As a manufacturer's representative, assisted customers throughout the Southeast in identifying, price quoting, and purchasing new HVAC equipment and accessories.
                 \item Sold and supported several lines and manufacturers including Bell and Gossett, Baltimore Aircoil, and Lochinvar.
                \item Assisted customers in equipment selection that best applied to their unique system needs. For instance, sizing pumps for clients based on need factors such as flow, head, power, and space requirements.
                \item Provided technical support and engineering knowledge for clients having problems with existing systems and equipment.
                \end{itemize}
 
 {\sl Project Estimator} \hfill Summer 2014 \\
                Padgett Group, 
               Canton, GA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Worked with Padgett Group, a Metro Atlanta mechanical services company.
                 \item Developed a database that generates energy cost and usage charts for baseline and cumulative periods. Analyzed peak electrical demand periods, in order to determine strategies that energy and demand costs could be reduced without capital expense to the client.
                \item   Observed installation of dialysis water cooling loops for several Emory Clinic locations, in order to reduce energy usage, and prolong the life of boiler equipment.
                \item Assisted field technicians in daily installation and maintenance work, learning about various HVAC systems and equipment such as cooling towers, chillers, boilers, and heat 		      exchangers, as well as automated control systems.
                \end{itemize}
 
                {\sl Supervisor Assistant} \hfill          May 2014-May 2015 \\
                 Town of Blacksburg, Blacksburg, VA
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Supervised day-to-day operations for Blacksburg Transit, the public transit department of the town. Primary duties were office support, dispatching, trip scheduling, and system oversight.
                 \item Secondary duties in opening/closing transit garage, customer assistance, assigning and fueling vehicles, preparing manifests and bulletins, accident documentation, and roadside response.
                 \end{itemize} 
 
 
\section{SKILLS} {\sl Languages \& Software:} C++, Java, Python, MATLAB/Octave, LabVIEW, Mathematica, Inventor, AutoCAD,
	      Access, ANSYS \\
               {\sl Certifications:} Class B Commercial Driver's License
 

%\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            %{\it Member}, Society of Asian Students and Engineers (SASE)
            %\begin{itemize}
            %\item Participated in community service projects sponsored by SASE.
            %\end{itemize}
	  %{\it Contributor}, Prof. Anthony Ferrar's Virginia Tech Green Initiative
	% \begin{itemize}
           % \item Recruited new members into the Green Initiative, which sought to reduce the carbon footprint of the Virginia Tech campus.


\end{resume}
\end{document}




